### 2012-06-06 trunk/paper-iswc-reification/querying.tex
polished Sections 5.1 and 5.2

	Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$ where $\symAllVariables$ is a set of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively.
	%We assume a set $\symAllVariables$ of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively. Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$.
A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
	For any {\TPplus} $tp \!=\! (s,p,o)$ we define $\fctVarsPlus{tp} \!:=\! \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.

@@

\begin{note}
		We note that any
		%Any
	(ordinary) SPARQL expression is a {\SPARQLplus} expression.
\end{note}

\todo{introduce $\fctVarsPlus{P}$ and $\fctTRefs{P}$ ...}

	\begin{tabular}{|c||c|c|} \hline
		{\SPARQLplus} expression $P$ &
		$\fctVarsPlus{P}$ &
		$\fctTRefs{P}$
		\\ \hline
		\hline
% 		{\TPplus} $(s,p,o)$ &
% 		$\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ &
% 		$\bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
% 		\\ \hline
		$(tp \OpAS ?v)$ &
		$\fctVarsPlus{tp} \cup \lbrace ?v \rbrace$ &
		$\fctTRefs{tp} \cup \lbrace tp \rbrace$
		\\ \hline
		$(P_1 \OpAND P_2)$ &
		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
		\\ \hline
		$(P_1 \OpOPT P_2)$ &
		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
		\\ \hline
		$(P_1 \OpUNION P_2)$ &
		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
		\\ \hline
		$(P' \OpFILTER R)$ &
		$\fctVarsPlus{P'} \cup \fctVars{R}$ &
		$\fctTRefs{P'}$
		\\ \hline
% 		$\OpSELECT_S(P')$ &
% 		$\fctVarsPlus{P'} \cup S$ &
% 		$\fctTRefs{P'}$
% 		\\ \hline
	\end{tabular}

@@

\noindent
\removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}

The following result shows that the query semantics introduced in this section is fully compatible to the usual SPARQL semantics (as defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus}
	and {\SPARQLplus}
may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.

\begin{proposition} \label{Proposition:EquivalenceOfSemantics}
	For any (ordinary) RDF graph $G$ and any (ordinary) SPARQL expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEval{P}{G}$.
\end{proposition}

\todo{...}

\begin{proposition}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
\end{proposition}

@@

\subsection{Using {\SPARQLplus} for Querying RDF Reification Based Metadata}
	%For RDF storage systems that do not support our {\RDFplus} data model (but the ordinary RDF data model), we define an alternative semantics for {\SPARQLplus}.
	In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an alternative semantics for {\SPARQLplus}. This alternative semantics enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.

>>>>

	Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$ where $\symAllVariables$ is a set of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively.
	%We assume a set $\symAllVariables$ of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively. Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$.
A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
%	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
%	For any {\TPplus} $tp \!=\! (s,p,o)$ we define $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.

@@

\begin{note}
		We note that any
		%Any
	(ordinary) SPARQL expression (as defined by P\'{e}rez et al.~\cite{Perez09:SemanticsAndComplexityOfSPARQL}) is a {\SPARQLplus} expression.
\end{note}

\noindent
For any {\SPARQLplus} expression $P$ we write $\fctTRefs{P}$ to denote the set of all {\TPplus}s embedded in a {\TPplus} in $P$; and $\fctVarsPlus{P}$ denotes the set of all variables mentioned in $P$ (including in embedded {\TPplus}s). Formally, if $P$ is a {\TPplus} $tp \!=\! (s,p,o)$,
then $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
If $P$ is not a {\TPplus}, then $\fctVarsPlus{P}$ and $\fctTRefs{P}$ are defined as follows:
	\par \vspace{1pt}
	\parbox{0.95\linewidth}{\centering
		\begin{tabular}{|c||c|c|} \hline
			{\SPARQLplus} expression $P$ &
			$\fctVarsPlus{P}$ &
			$\fctTRefs{P}$
			\\ \hline
			\hline
% 			{\TPplus} $(s,p,o)$ &
% 			$\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ &
% 			$\bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
% 			\\ \hline
			$(tp \OpAS ?v)$ &
			$\fctVarsPlus{tp} \cup \lbrace ?v \rbrace$ &
			$\fctTRefs{tp} \cup \lbrace tp \rbrace$
			\\ \hline
			$(P_1 \OpAND P_2)$ &
			$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
			$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
			\\ \hline
			$(P_1 \OpOPT P_2)$ &
			$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
			$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
			\\ \hline
			$(P_1 \OpUNION P_2)$ &
			$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
			$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
			\\ \hline
			$(P' \OpFILTER R)$ &
			$\fctVarsPlus{P'} \cup \fctVars{R}$ &
			$\fctTRefs{P'}$
			\\ \hline
% 			$\OpSELECT_S(P')$ &
% 			$\fctVarsPlus{P'} \cup S$ &
% 			$\fctTRefs{P'}$
% 			\\ \hline
		\end{tabular}
	}
	\par

@@

\noindent
% \removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
% 
We emphasize that our definitions in this section resemble the definitions with which
	%P\'{e}rez et al.~define
the evaluation function $\fctEval{\cdot}{ }$ for ordinary SPARQL
	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
	expressions is defined~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
As the primary difference we note that the definitions for SPARQL are based on so called \emph{solution mapping}s, that are, partial mappings $\mu : \symAllVariables \rightarrow \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$, whereas we use valuations $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$. However, any valuation
	%$\eta$ for which $\forall \, ?v \in \fctDom{\eta} : \eta(?v) \notin \symAllTriples$,
	that binds variables only to URIs, blank nodes, or literals (but not to {\RDFplusTriple}s),
may also be understood as a solution mapping. Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is fully compatible to the usual SPARQL semantics (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.

\begin{proposition} \label{Proposition:EquivalenceOfSemantics}
	For any
		%(ordinary)
	RDF graph $G$ and any
		%(ordinary)
	SPARQL
		%expression $P$
		expr.~$P$
	holds $\fctEvalPlus{P}{G} \!=\! \fctEval{P}{G}$.
\end{proposition}

\todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}

\begin{proposition} \label{Proposition:JustificationForDataMinimality2}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
\end{proposition}

@@

\subsection{Using {\SPARQLplus} for Querying RDF Reification Based Metadata}

In addition to the {\SPARQLplus} semantics defined in the previous section, we now define
	%an alternative semantics for {\SPARQLplus}. This alternative semantics
	a function for converting {\SPARQLplus} queries to SPARQL queries. This conversion function
enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.

### 2012-06-06 trunk/paper-iswc-reification/rep.tex
polished Sections 5.1 and 5.2

\section{Representation}
Syntax 
Expressed tersely as:
  <<:SAP :bought :sybase>> dc:source reuters:us-sybase .
Statements are “wrapped” by << … >> 
Turtle Extension
<<:SAP :bought :sybase>> dc:source reuters:us-sybase ;
			  dc:created “1995-01-07” ;
                        		 dc:author  “James R. Jones“ .

-	The statement can appear in either the subject or object position.
-	Recursion in statements is allowed
-	But depth is shallow in practice
Semantics

>>>>

\section{Data Model} \label{Section:DataModel}

In this section we introduce
	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
	our data model which we call {\RDFplus}. This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}. {\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
% In the following we \todo{...}

% Main purposes of our data model: 1.)~it allows for a more compact representation; 2.)~it allows for efficient processing
% with {\RDFplus} our goal is to extend/expand the applicability/usefulness/usability of such triples for cases where ...

\subsection{Concepts}

We assume
	%\removable{three,}
pairwise disjoint sets $\symAllURIs$ (all URI references), $\symAllBNodes$ (blank nodes), and $\symAllLiterals$ (literals).
	As usual, an \emph{RDF triple} is a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and an \emph{RDF graph} is a set of RDF triples.
	%As usual, a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ is an \emph{RDF triple}.
% A set of RDF triples is an \emph{RDF graph}.

{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple. We shall interpret the embedding triple as a statement about the embedded triple. An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
	%Therefore, the model should allow for nesting.
%
	%As a basis for formalizing
	To formalize
such kind of (nested) embedding we
	%introduce
	define
a set $\symAllTriplesInfinite := (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
%
	As a basis for ruling
	%To rule
out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
	is an arbitrary
	%may be any
natural number): A tuple $(s,p,o) \in \symAllTriplesInfinite$ is $k$-nested if either 1.)~$k=0$ and
	%$(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$
	$(s,p,o)$ is an RDF triple
or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTriplesInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested. Using $k$-nestedness we now define our extended notion of triples%
	.
	%:

An \emph{{\RDFplusTriple}} is a tuple $t \in \symAllTriplesInfinite$ for which exists a natural number $k$ such that $t$ is $k$-nested; to denote the set of all {\RDFplusTriple}s we write $\symAllTriples$ (i.e.~$\symAllTriples \subset \symAllTriplesInfinite$).
For any {\RDFplusTriple} $t=(s,p,o)$ we define
	$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \big\lbrace x' \in \fctTermsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
	%$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \bigcup_{x \in \lbrace s,o \rbrace \cap \symAllTriples} \fctTermsPlus{x}$.
%Furthermore, we write $\fctTRef{t}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in $t$; formally: $\fctTRef{t} := \bigl( \lbrace s,o \rbrace \cap \symAllTriples \bigr) \cup \big\lbrace t' \in \fctTRef{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
We call an {\RDFplusTriple}
	$t=(s,p,o)$ for which $s \in \symAllTriples$ or $o \in \symAllTriples$,
	%$t$ for which $\fctTRef{t} = \emptyset$,
a \emph{metadata triple}%
	%; note that any other {\RDFplusTriple} is an ordinary RDF triple.
	.

A set of {\RDFplusTriple}s is an \emph{\RDFplusGraph}. Overloading function $\symTermsPlusFct$, for any {\RDFplusGraph} $G$ we define $\fctTermsPlus{G} := \bigcup_{t \in G} \fctTermsPlus{t}$. Furthermore, for {\RDFplusGraph} $G$, we write $\fctTRefs{G}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in {\RDFplusTriple}s of $G$; hence $\fctTRefs{G} := \fctTermsPlus{G} \cap \symAllTriples$.

% Any {\RDFplusTriple} that is embedded in another {\RDFplusTriple} is also assumed to be (implicitly) contained in data that contains the embedding triple. To make this assumption explicit we introduce an operation that (recursively) unnests {\RDFplusTriple}s: Let $t=(s,p,o)$ be an {\RDFplusTriple}, then $\fctClose{t}$ is a set of {\RDFplusTriple}s that is defined as follows:
% \begin{equation*}
% 	\fctClose{t} := \big\lbrace t' \,\big|\, t' = t \text{ or } \exists \, t^* \in \lbrace s,o \rbrace \cap \symAllTriples : t' \in \fctClose{t^*} \big\rbrace
% \end{equation*}
% Overloading
% 	function $\symCloseFct$,
% 	%notation,
% for any {\RDFplusGraph} $G$ we define $\fctClose{G} := \bigcup_{t \in G} \fctClose{t}$.

% While syntactically {\RDFplusTriple}s and {\TRef}s are the same, they represent different concepts: {\RDFplusTriple}s may be interpreted as statements (similar to RDF triples) whereas a {\TRef} denotes an {\RDFplusTriple}
% 	%that is embedded in other {\RDFplusTriple}s.
% 	for the purpose of making a statement about it.
% %
% 	\removable{Hence, trefs may be understood as a particular type of name for {\RDFplusTriple}s.}
% However, since {\TRef}s carry all elements of the {\RDFplusTriple}s they denote, it is possible to obtain such a triple from its reference: We introduce a bijective function $\symDerefFct$ that maps the set of {\TRef}s to the set of all {\RDFplusTriple}s and that is defined as follows: Let $r=(s,p,o) \in \symAllTRefs$ be an arbitrary {\TRef}, then $\fctDeref{r}$ is the {\RDFplusTriple} $(s,p,o)$.

% \todo{$G$ and $\fctClose{G}$ are semantically equivalent!!}
\todo{$G$ and $G \cup \fctTRefs{G}$ are semantically equivalent!!}

\subsection{Interpretation}

Let $G$ be an {\RDFplusGraph}. For \Todo{converting}{introduce this subsection (explain the purpose of the conversion function defined here)} $G$ into a set of RDF triples we assume a bijective function $id : \fctTRefs{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRefs{G} |$ and $B \cap \fctTerms{G} = \emptyset$. Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$). Furthermore, we introduce
	%an injective function $id^* : \fctTermsPlus{G} \rightarrow \fctTermsPlus{G} \cup B$
	another bijective function $id^*\! : \fctTermsPlus{G} \rightarrow B \cup \bigl( \fctTermsPlus{G} \!\setminus\! \fctTRefs{G} \bigr)$
that is defined as follows: Let $x \in \fctTermsPlus{G}$. If $x \in \symAllTriples$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTriples$ then $id^*\!(x) := x$.
%
Using $id^*$, for any $t = (s,p,o) \in \fctTRefs{G}$ we define:
\begin{align*}
	\mathrm{reif}\bigl( t \bigr) := \big\lbrace
		& (id^*\!(t),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
		(id^*\!(t),\mathTinyRDF{rdf\!:\!subject},id^*\!(s)), \\
		& (id^*\!(t),\mathTinyRDF{rdf\!:\!predicate},id^*\!(p)),
		(id^*\!(t),\mathTinyRDF{rdf\!:\!object},id^*\!(o))
	\big\rbrace
\end{align*}

\noindent
For any {\RDFplusTriple} $t = (s,p,o) \in G$ we define:
\begin{equation*}
	\fctDescent{t} := \begin{cases}
\vspace{1mm}
		\big\lbrace (id(s),p,o) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s} & \text{if $s \in \symAllTriples$ and $o \notin \symAllTriples$,} \\
\vspace{1mm}
		\big\lbrace (s,p,id(o)) \big\rbrace \cup \mathrm{reif}(o) \cup \fctDescent{o} & \text{if $s \notin \symAllTriples$ and $o \in \symAllTriples$,} \\
\vspace{1mm}
		\begin{minipage}[c]{55mm}\vspace{1mm}
			$\big\lbrace (id(s),p,id(o)) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s}$ \\
			\hspace*{27.5mm}$\cup \, \mathrm{reif}(o) \cup \fctDescent{o}$
		\end{minipage} & \text{if $s \in \symAllTriples$ and $o \in \symAllTriples$,} \\
		\big\lbrace (s,p,o) \big\rbrace & \text{else} .
\end{cases}
\end{equation*}

\noindent
\Todo{Finally}{add some more text here}:
\begin{equation*}
	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
\end{equation*}

\begin{example}
	Let $G_\mathsf{ex} = \lbrace t_\mathsf{ex} \rbrace$ be an {\RDFplusGraph} that consists of a single {\RDFplusTriple} $t_\mathsf{ex} = \bigl( (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}), \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf} \bigr)$.
% 	The result of converting $G_\mathsf{ex}$ to an RDF graph is:
% 	\begin{align*}
% 		\fctDescent{G_\mathsf{ex}} = \big\lbrace
% 			& (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}),
% 			(b, \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf}), \\
% 			& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
% 			(b,\mathTinyRDF{rdf\!:\!subject},\mathTinyRDF{ex:olaf}), \\
% 			& (b,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{foaf:name}),
% 			(b,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{"Olaf"})
% 		\big\rbrace
% 	\end{align*}
	The result of converting $G_\mathsf{ex}$ to an RDF graph $\fctDescent{G_\mathsf{ex}}$ is (in Turtle notation, prefix declarations omitted):
	\begin{footnotesize}%
	\begin{verbatim}
		 ex:olaf foaf:name "Olaf" .
		 _:b dct:source ex:olaf ; rdf:type rdf:Statement ;
		     rdf:subject ex:olaf ; rdf:predicate foaf:name ; rdf:object "Olaf" .
	\end{verbatim}%
	\end{footnotesize}
\end{example}

\noindent
Based on the conversion function, it is possible to interpret any {\RDFplus} model via the usual RDF semantics as defined in~\cite{Hayes04:RDFsemantics}.

\begin{proposition} \label{Proposition:JustificationForDataMinimality1}
	For any {\RDFplusGraph} $G$ it holds $\fctDescent{G} = \fctDescent{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
\end{proposition}

\subsection{Representation}
\todo{briefly introduce our extension for Turtle and explain how this extension is related to {\RDFplus} and how it should be parsed by systems that do not ``understand'' {\RDFplus}}

	\begin{footnotesize}%
	\begin{verbatim}
		 <<ex:olaf foaf:name "Olaf">> dct:source ex:olaf .
	\end{verbatim}%
	\end{footnotesize}

\todo{From a didactic point of view it may be better to move this subsection to the beginning of Section~\ref{Section:DataModel}}
